---
title: "How_to_Perceptual_Maps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How_to_Perceptual_Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HelpMe)
```

# Simple case

We use **all** rows and columns of the file child_red.csv.

All outputs are exported in the working directory.

child_red_coord.csv and child_red_data.csv are saved.

If Officer and Rvg are installed, the pptx child_red.pptx is created.

```{r}
res.ca <- HelpMe::create_CA("child_red.csv")
HelpMe::export_CA(res.ca)
if (HelpMe::check_pptx()) {save_CA_pptx(res.ca, "child_red.pptx")}
```

# Complex case

## flipping axes
Sometimes you want to plot the map with flipped axes-
In this case, you have to flip before exporting and printing

```{r}
res.ca <- HelpMe::create_CA("child_red.csv")
# first show original map
HelpMe:::plot_ISCA(res.ca)
# example on Dim 1
# extract the data for the map from the objevct res.ca
df <- res.ca$PM_coord
df$`Dim 1` <- -1 *df$`Dim 1` #flip
#resave the correct coordinates into the object res.ca
res.ca$PM_coord <- df
# plot the new map
HelpMe:::plot_ISCA(res.ca)
#export the coordinates used for the flipped map
HelpMe::export_CA(res.ca)
```

## removing row or columns

We don't use the **first** row and **4th** column of the file child_red.csv.

All outputs are exported in the *output* directory.

As we use *title :* MyCA_coord.csv and MyCA_data.csv and MyCA_eigen are saved.

If Officer and Rvg are installed, the pptx Mypptx.pptx is created using the template from the package HelpMe.

```{r}
getwd()
res.ca <- HelpMe::create_CA("child_red.csv", row.sup = 1, col.sup = 4, title = "MyCA")
dir.create("output")
HelpMe::export_CA(res.ca, "output")
HelpMe:::plot_ISCA(res.ca)
```


